The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2009-08-04 script/en/chapters/primes.tex
CT script, chap 4: chapter appendixes now as normal sections; all Sage examples appear in list at the end of the document and in the PDF reader frame; smaller corrections (en only)
reduced number of pdfTeX warnings (hyperlink related) from 615 to 15; moved index{...} out of headings

% --------------------------------------------------------------------------
\vskip +10 pt
\subsection{Carmichael numbers\index{Number!Carmichael}}
As mentioned \hyperlink{HT-Carmichael-number01}{above} in
chapter~\ref{L-Carmichael-number01} not all Carmichael numbers are prime.

% --------------------------------------------------------------------------
\vskip +10 pt
\subsection{Pseudo prime numbers%
\index{Prime number!pseudo prime}\index{Number!pseudo prime}%
}
See \hyperlink{HT-Pseudoprimenumber01}{above} in
chapter~\ref{L-Pseudoprimenumber01}.

% --------------------------------------------------------------------------
\vskip +10 pt
\subsection{Strong pseudo prime numbers%
\index{Prime number!strong pseudo prime}\index{Number!strong pseudo prime}%
}
See \hyperlink{HT-Strongpseudoprimenumber01}{above} in
chapter~\ref{L-Strongpseudoprimenumber01}.

@@

The following section contains Sage source code related to contents of 
the ``\nameref{Label_Kapitel_2}'' chapter (chap. no. \ref{Label_Kapitel_2}).

>>>>

% --------------------------------------------------------------------------
\vskip +10 pt
\subsection{Carmichael numbers}\index{Number!Carmichael}
As mentioned \hyperlink{HT-Carmichael-number01}{above} in
chapter~\ref{L-Carmichael-number01} not all Carmichael numbers are prime.

% --------------------------------------------------------------------------
\vskip +10 pt
\subsection{Pseudo prime numbers}
\index{Prime number!pseudo prime}\index{Number!pseudo prime}
See \hyperlink{HT-Pseudoprimenumber01}{above} in
chapter~\ref{L-Pseudoprimenumber01}.

% --------------------------------------------------------------------------
\vskip +10 pt
\subsection{Strong pseudo prime numbers}
\index{Prime number!strong pseudo prime}\index{Number!strong pseudo prime}
See \hyperlink{HT-Strongpseudoprimenumber01}{above} in
chapter~\ref{L-Strongpseudoprimenumber01}.

@@

\noindent Below is Sage source code related to contents of the
chapter~\ref{Label_Kapitel_2} (``\nameref{Label_Kapitel_2}'').

### 2009-08-04 script/en/script-en.tex
added argument to example and remark definitions
fixed various table to use the table environment and caption
CT script: added new cover page (de+en); chap 4: appendix with sage samples: changed the name of some self-defined functions... - not finished yet (en only)
reduced number of pdfTeX warnings (hyperlink related) from 615 to 15; moved index{...} out of headings

\documentclass[a4paper,11pt,oneside]{book}
\setlength{\fboxrule}{.5mm}
\setlength{\fboxsep}{1.75mm}
\setlength{\footnotesep}{6pt}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,bookmarksnumbered=true]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{fancyvrb}
\usepackage{makeidx}
\usepackage[pdftex]{graphicx}

\usepackage[flushmargin]{footmisc}
\usepackage{fullpage}
\usepackage{url}
% Literaturverzeichnis kapitelweise
\usepackage[labelstoglobalaux]{bibunits} % ohne labelstoglobalaux scheint man thebibilograpy und bibtex nicht mischen zu können
%\bibliographyunit[\section] % bibunits für das ganze Dokument aktivieren
\defaultbibliography{references}
\defaultbibliographystyle{abbrv}
\usepackage{float}
\floatstyle{ruled}
\newfloat{sagecode}{!h}{loc}[chapter]
\floatname{sagecode}{Sample}

@@

% \setlength{\textwidth}{460 pt}
% \hoffset-0.7in
\newtheorem{definition}{Definition}[section]
%\newcommand{\href}[2]{#2}
\newcommand{\hypertag}[2]{#1}
%\newcommand{\hyperlink}[2]{#2}
%\newcommand{\hypertarget}[2]{#2}
\newtheorem{theorem}{Theorem}[section]
\newenvironment{Proof}[1]
  {\textbf{Proof #1} \\}
  {\hfill$\Box$ \\}
\newenvironment{example}{\noindent\textbf{Example.}}{}
\newenvironment{remark}{\noindent\textbf{Comment.}}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{ % Keine Leerzeilen, sonst Meldung: "Paragraph ended before \title was complete."
	{\Huge The CrypTool Script: \\
	 \vspace{5pt}
	Cryptography, Mathematics and More} \\
        \vspace{20pt}
	{\LARGE	Background reading\\ 
        for the free e-learning program CrypTool} \\
        \vspace{15pt}
        {\large (10th edition -- distributed with CrypTool version 1.4.30)}
        \vspace{180pt}
}

@@

>>>>

\documentclass[a4paper,11pt,oneside]{book}
\setlength{\fboxrule}{.5mm}
\setlength{\fboxsep}{1.75mm}
\setlength{\footnotesep}{6pt}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{fancyvrb}
\usepackage{makeidx}
\usepackage[pdftex]{graphicx}
\usepackage{pdfpages}   % SR_2009: added new cover

\usepackage[flushmargin]{footmisc}
\usepackage{fullpage}
\usepackage{url}
% Literaturverzeichnis kapitelweise
\usepackage[labelstoglobalaux]{bibunits} % ohne labelstoglobalaux scheint man thebibilograpy und bibtex nicht mischen zu können
%\bibliographyunit[\section] % bibunits für das ganze Dokument aktivieren
\defaultbibliography{references}
\defaultbibliographystyle{abbrv}
\usepackage{float}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,bookmarksnumbered=true,pdfpagelabels,hypertexnames=false]{hyperref}
%To reduce the number of hyperlink related 'pdfTeX warning's we use options 
%pdfpagelabels and hypertexnames=false and place hyperref after float.
%Option debug helps finding problems.

\floatstyle{ruled}
\newfloat{sagecode}{!h}{loc}[chapter]
\floatname{sagecode}{Sage sample}

@@

% \setlength{\textwidth}{460 pt}
% \hoffset-0.7in
\newtheorem{definition}{Definition}[section]
%\newcommand{\href}[2]{#2}
\newcommand{\hypertag}[2]{#1}
%\newcommand{\hyperlink}[2]{#2}
%\newcommand{\hypertarget}[2]{#2}
\newtheorem{theorem}{Theorem}[section]
\newenvironment{Proof}[1]
  {\textbf{Proof #1} \\}
  {\hfill$\Box$ \\}
\newenvironment{example}[1]{\noindent\textbf{Example#1}}{}
\newenvironment{remark}[1]{\noindent\textbf{Comment#1}}{}

% Define title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{ % Keine Leerzeilen, sonst Meldung: "Paragraph ended before \title was complete."
	{\Huge The CrypTool Script: \\
	 \vspace{5pt}
	Cryptography, Mathematics and More} \\
        \vspace{20pt}
	{\LARGE	Background reading\\ 
        for the free e-learning program CrypTool} \\
        \vspace{15pt}
        {\large (10th edition -- distributed with CrypTool version 1.4.30)}
        \vspace{180pt}
}

@@

\includepdf[page=1]{figures/coverv1_en.pdf}    % SR_2009: added new cover
